Dynamic Walking and Whole-Body Motion Planning for Humanoid Robots: an Integrated Approach

### 2012-12-05 paper.tex
Update table format.
Move benchmark plots to appendix.

\usepackage{float}
\restylefloat{table}
\usepackage{array} 
\usepackage{mdwmath}
\usepackage{mdwtab}

@@

\textbf{The motion planning algorithms presented in this paper have been
implemented using KineoWorks\texttrademark \cite{laumond2006kcs}. The
planning times have been measured on an Intel Core~2~Duo 2.13~GHz PC
with 2~GB of RAM. Evaluation of the randomized algorithm has been
conducted by executing 500 trials on each scenario using two flavors of
RRT: the classic RRT and IPP-RRT \cite{FERR04A}. We present the
results in Fig. \ref{fig:rrt-it}, \ref{fig:rrt-t}, \ref{fig:rrt-n}, as
well as in Extension 4 for the raw data.}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.8\linewidth]{plots/rrt-it.eps}
\caption{Number of RRT iterations $it$ for the floating objects and the
  shelf scenarios, using two variants of RRT. Mean $\overline{it}$,
  standard deviation $\sigma_{it}$, minimum and maximum values are
  represented.}
\label{fig:rrt-it}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=0.8\linewidth]{plots/rrt-t.eps}
\caption{RRT computation time $t$ for the floating objects and the shelf
  scenarios, using two variants of RRT. Mean $\overline{t}$, standard
  deviation $\sigma_{t}$, minimum and maximum values are represented.}
\label{fig:rrt-t}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=0.8\linewidth]{plots/rrt-n.eps}
\caption{Number of tree nodes $n$ for the floating objects and the
  shelf scenarios, using two variants of RRT. Mean $\overline{n}$,
  standard deviation $\sigma_{n}$, minimum and maximum values are
  represented.}
\label{fig:rrt-n}
\end{figure}

@@

\appendix
\section{Index to Multimedia Extensions}

\begin{table}[H]
\begin{tabular}{c c m{0.7\linewidth}}
Extension & Type & Description \\
\hline
1 & Video & Example of a constrained motion planning result executed
on HRP-2. \\
2 & Video & Chairs scenario: solution of whole-body planning executed
on HRP-2. \\
3 & Video & Shelf scenario: solution of whole-body planning executed
in simulation and on HRP-2. \\
4 & Data & Raw data of sliding motion planning benchmarks for all
scenarios. \\
\end{tabular}
\end{table}

>>>>

\usepackage{float}
\usepackage{array} 
\usepackage{mdwmath}
\usepackage{mdwtab}

@@

\textbf{The motion planning algorithms presented in this paper have
  been implemented using KineoWorks\texttrademark
  \cite{laumond2006kcs}. The planning times have been measured on an
  Intel Core~2~Duo 2.13~GHz PC with 2~GB of RAM. Evaluation of the
  randomized algorithm has been conducted by executing 500 trials on
  each scenario using two flavors of RRT: the classic RRT and IPP-RRT
  \cite{FERR04A}. We present the results in Appendix \ref{app:bench},
  Fig. \ref{fig:rrt-it}, \ref{fig:rrt-t}, \ref{fig:rrt-n}, as well as
  in Extension 4 for the raw data.}

@@

@@

\appendix
\section{Sliding Motion Planning Benchmarks}
\label{app:bench}

\begin{figure}[H]
\centering
\includegraphics[width=0.8\linewidth]{plots/rrt-it.eps}
\caption{Number of RRT iterations $it$ for the floating objects and the
  shelf scenarios, using two variants of RRT. Mean $\overline{it}$,
  standard deviation $\sigma_{it}$, minimum and maximum values are
  represented.}
\label{fig:rrt-it}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.8\linewidth]{plots/rrt-t.eps}
\caption{RRT computation time $t$ for the floating objects and the shelf
  scenarios, using two variants of RRT. Mean $\overline{t}$, standard
  deviation $\sigma_{t}$, minimum and maximum values are represented.}
\label{fig:rrt-t}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.8\linewidth]{plots/rrt-n.eps}
\caption{Number of tree nodes $n$ for the floating objects and the
  shelf scenarios, using two variants of RRT. Mean $\overline{n}$,
  standard deviation $\sigma_{n}$, minimum and maximum values are
  represented.}
\label{fig:rrt-n}
\end{figure}

\section{Index to Multimedia Extensions}

\begin{table}[H]
\begin{tabular}{c c m{0.7\linewidth}}
\hline
Extension & Type & Description \\
\hline
1 & Video & Example of a constrained motion planning result executed
on HRP-2. \\
2 & Video & Chairs scenario: solution of whole-body planning executed
on HRP-2. \\
3 & Video & Shelf scenario: solution of whole-body planning executed
in simulation and on HRP-2. \\
4 & Data & Raw data of sliding motion planning benchmarks for all
scenarios. \\
\hline
\end{tabular}
\end{table}
